Dynein project log

### 2016-12-29 thesis_stuff/thesis_stuff.tex
Add feature to save disc space by only printing movie data when program crashes.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & trying to find good springs for binding & this one seems to keel over, not strong enough springs\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, but this one seems to also keel over, so springs not strong enough\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & trying to find good springs for binding & Looks good, takes lots of steps! Too many?\\\hline
    22.1 & 11.1 & 5000 & 5000 & 4.65 & 4.65 & 4.65 & trying to find good springs for binding & Seems very rigid, but might have the right probabilities\\\hline
  \end{tabular}
\end{center}
